Summary

### 2015-10-24 inst/examples/summary.Rmd
ok

missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

>>>>

# Need to use this trick to have NAs for all data types
missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
```

Percentage of non-NA entries among all documents in the preprocessed data (note that in some cases a significant fraction of this information is missing already in the raw data)

```{r missingb, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

Fields of special interest: success percentage compared to non-NA entries in the raw data:

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
dfs <- df %>% select(publication_place, country, published_in, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2)
missing <- 100*apply(dfs, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])

theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)

dfs <- df.orig %>% select(publication_place, note_year, corporate, physical_extent, physical_dimension)
missing <- 100*apply(dfs, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])

theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with raw data (%)")
print(p)
```
